An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-31 measure.tex
more stylistic
are we missing proper references for CDE and Docker?

{\bf Capturing Dependencies.}  The Unix {\tt ptrace} mechanism
allows a tracing process to observe all of the system calls performed by
an application, inferring each of the resources upon which an application
depends.  We have extended two existing tracing tools in order to capture
dependency information at the granularity of files and directories. 
Dependency may refer to source code, if available, or a binary.

Parrot is a virtual filesystem access tool which
is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
replacing selected operations with remote accesses.  As a side-effect, Parrot is
also able to modify the filesystem namespace in arbitrary ways according to user
needs.  Parrot is particularly used in the high-energy physics community
to provide remote access to application software via CVMFS.
To capture dependencies, we made small modifications to Parrot to record
the logical name of every file accessed by an application into an external
dependency list.  After execution is complete, a second tool is used to copy
all of the named dependencies into a package.

PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.   PTU uses the CDE technology to observe system calls, but takes a snapshot of every file at the point of access.  In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.  PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.  Because PTU is focused solely on the problem of preservation, therefore it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.

@@

Many possible heuristics exist for creating the preserved package
from the dependency list.  We have implemented three:
In a {\bf shallow copy}, we copy only
the exact dependencies.  Where a directory was listed, a directory is created and populated with empty files as placeholders to facilitate a directory listing.  In a {\bf medium copy},every file in every directory mentioned by the application is preserved one level deep.  In a {\bf deep copy}, every file in every directory mentioned by the application is copied recursively.  Obviously, the more aggressive the preservation, the larger the package, but also the greater the possibility that the package can be adapted to other uses.  Other approaches to package generation might including generating the union
of multiple dependency sets, or allowing an expert user to manually add
and remove dependencies.

@@

{\bf Distribution and Deployment.}
Once generated, application packages must be collected, curated, and made
available through publically shared repositories.  Currently, a 
wide variety of services and efforts exist in order to share binary objects in this way,
and so we assume such multiple services will be available in the future.

@@

 % Docker images
\vspace{5pt}
\noindent{\bf Linux Containers and Docker Images:} 
Linux Containers provide multiple isolated instances of execution on top of the same kernel through OS-level virtualization. Thus they can be used to persist the captured packages into images. Using such containers, Docker now allows for the preservation of the image in a more user-friendly way. Docker also provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images. The image can be preserved along with dockerfiles, which are text files that contain all the commands to build a Docker image. Similar to shell scripts, the computational section can help other provisioning tools (e.g. Chef, Puppet).  The text section, written for for human consumption, is more suited for use with a version management system such as subversion or git, which can track any changes made to the Dockerfile. Thus dockerfiles can be used to preserve the namelist of Parrot packages and provenance description in PTU. Docker is integrated with a continuous build environment that will not only check and validate the version of the software in present use, but also make use of a more recent version to build application software.

>>>>

{\bf Capturing Dependencies.}  
The Unix {\tt ptrace} mechanism
allows a tracing process to observe all of the system calls performed by
an application, inferring each of the resources upon which an application
depends.  We have extended two existing tracing tools in order to capture
dependency information at the granularity of files and directories. 
Dependency may refer to source code, if available, or a binary file.

Parrot is a virtual filesystem access tool which
is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CernVM-FS. It works by trapping system calls through the {\tt ptrace} interface and replacing selected operations with remote accesses.  As a side-effect, Parrot is
also able to modify the filesystem namespace in arbitrary ways according to user
needs. Parrot is particularly used in the high-energy physics community
to provide remote access to application software via CernVM-FS.
To capture dependencies, we made small modifications to Parrot to record
the logical name of every file accessed by an application into an external
dependency list.  After execution is complete, a second tool is used to copy
all of the named dependencies into a package.

The second tool, PTU~\cite{pham2014framework}, is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.   PTU uses the lightweight virtualization software tool Code Data Environment (CDE) to observe system calls, but takes a snapshot of every file at the point of access. In addition to files, PTU records \emph{metadata} about the execution environment, such as Linux kernel version, application version, and dynamic library versions by using standard Unix commands.  PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.  Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.

@@

Many possible heuristics exist for creating the preserved package
from the dependency list.  We have implemented three:
In a {\bf shallow copy}, we copy only
the exact dependencies.  Where a directory was listed, a directory is created and populated with empty files as placeholders to facilitate a directory listing.  In a {\bf medium copy}, every file in every directory mentioned by the application is preserved one level deep.  In a {\bf deep copy}, every file in every directory mentioned by the application is copied recursively.  Obviously, the more aggressive the preservation, the larger the package, but also the greater the possibility that the package can be adapted to other uses.  Other approaches to package generation might including generating the union
of multiple dependency sets, or allowing an expert user to manually add
and remove dependencies.

@@

{\bf Distribution and Deployment.} Once generated, application packages must be collected, curated, and made
available through publicly shared repositories.  Currently, a 
wide variety of services and efforts exist in order to share binary objects in this way,
and so we assume such multiple services will be available in the future.

@@

 % Docker images
\vspace{5pt}
\noindent{\bf Linux Containers and Docker Images.} 
Linux Containers provide multiple isolated instances of execution on top of the same kernel through OS-level virtualization. Thus they can be used to persist the captured packages into images. Using such containers, Docker now allows for the preservation of the image in a more user-friendly way. Docker also provides portable deployment of containers across platforms, documentation of packages in a scriptable format, and versioning of container images. The image can be preserved along with \em{dockerfiles}, which are text files containing all the commands to build a Docker image. Similar to shell scripts, the computational section can help other provisioning tools (e.g. Chef, Puppet).  The text section, written for human consumption, is more suited for use with a version management system such as subversion or git, which can track any changes made to the dockerfile. Thus dockerfiles can be used to preserve the namelist of Parrot packages and provenance description in PTU. Docker is integrated with a continuous build environment that will not only check and validate the version of the software in present use, but also make use of a more recent version to build application software.
